Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-18 paper/paper.tex
Add to characterising section inside the paper

There are multiple platforms for providing such issue tracking systems, among which
the most popular are Jira \cite{jira} and Bugzilla \cite{bugzilla}. For both platforms,
the tickets are split into two main categories: feature requests (i.e. feature to be 
implemented into the system) and bug reports (i.e. issue encountered by an end user or
discovered by a developer in the codebase). Regardless of the type of ticket, they provide
various types of information that can be filled in by the reporter, including:
  \begin{itemize}
    \item summary - short description of the feature to be implemented/encountered bug;
    \item description - longer textual field which goes into more detail regarding the ticket;
    it can include various types of information, such as stack traces or steps to reproduce a bug;
    \item attachments - screenshots, snippets of code or configuration files that might help
    close the ticket faster;
    \item comments - each ticket can have any number of comments where the people interested in 
    it can talk about what might have caused the bug, how to fix it etc.
  \end{itemize}

Even though tickets provide such comprehensive information regarding a specific task, studies have shown 
that fixing bugs is one of the most common tasks performed by developers \cite{latoza2006maintaining}. One of
the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
decreased customer satisfaction and overall poor performance.

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. As there are many 
fields in a ticket, there are numerous unanswered questions: do stack traces have an influence on the quality
of a ticket? What about attachments and whether a screenshot is more helpful than a snippet of code? Does a negative sentiment
drawn from comments increase or decrease the time taken to solve a bug? How does grammar correctness influence the 
communication friction?

@@

Also, in order to validate our findings, the statistics command fetches all the data from the database and

@@

>>>>

There are multiple platforms for providing such issue tracking systems, among which
the most popular are Jira \cite{jira} and Bugzilla \cite{bugzilla}. For both platforms,
the tickets are split into two main categories: feature requests (i.e. feature to be 
implemented into the system) and bug reports (i.e. issue encountered by an end user or
discovered by a developer in the codebase). Regardless of the type of ticket, they possess
various information that can be filled in by the reporter (i.e. person who created the ticket; 
can be both an end user or a developer in the team), providing the developers
a detailed view of what is requested or what went wrong.

Even though tickets provide such comprehensive data regarding a specific task, studies have shown 
that fixing bugs is one of the most common tasks performed by developers \cite{latoza2006maintaining}. One of
the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
decreased customer satisfaction and overall poor performance.

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. As there are many 
fields in a ticket, there are numerous unanswered questions, such as whether stack traces have an influence on the quality
of a ticket?

@@

Also, in order to validate our findings, the statistics command fetches all the data from the database and runs two types of 
tests: Welch's T Test \cite{welch1947generalization} for analysing categorical data (e.g. has/does not have attachments)
and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
grammar correctness scores change \emph{Time-To-Complete}).

@@

The data that we collected is stored, as previously mentioned, in a Bolt database instance which is around 6 GB in size. 
All tickets are stored as key-value pairs, where the key is the ticket's unique ID (e.g. KAFKA-100) and the value is the 
JSON encoded representation of the ticket. The tickets stored have the following fields available for investigation:
\begin{itemize}
  \item attachments - files or images attached to tickets;
  \item summary - short description of the ticket;
  \item description - more detailed information regarding what is requested or what bug was encountered;
  \item time estimate - estimated number of hours to complete the task (set by triagers or developers);
  \item time spent - time period between opening the ticket and a specific point in time;
  \item created timestamp;
  \item issue status - jira specific statuses, including Open, Closed, Awaiting Review, Patch Submitted;
  \item due date - optional deadline for when the ticket should get closed;
  \item comments - discussion around the ticket conducted by developers, end users, triagers;
  \item priority - it can range from low priority (minor) to critical/blocker;
  \item issue type - specific Jira field that specifies whether the ticket is either a bug, a feature request or a general task.
\end{itemize}

There are other fields that can be configured inside Jira, including custom fields, but we did not collect them as they would not 
have been helpful in conducting the analysis. However, in addition to the fields we saved, we also store grammar correctness scores 
(i.e. number of grammar mistakes identified in summary, description and comments), sentiment scores (i.e. sentiment drawn from summary 
and description), whether they have steps to reproduce, if stack traces are present and number of words in comments, summary and description. 
Even though all of them, apart from grammar and sentiment scores, can be computed locally, we store them because of performance issues
due to the very large size of the database.
